Northern Pikeminnow Predation on Juvenile Chinook Salmon and Potential Impacts to Local Populations

### 2021-11-15 analysis/paper/paper.Rmd
added tables showing abundance data used in estimators.

>>>>

```{r abund-data-lp}
LP_mod %>%
  select(event_name, species, data) %>%
  distinct() %>%
  unnest(data) %>%
  mutate(across(event_name,
                ~ str_replace(., "_", " "))) %>%
  rename(`Sampling Event` = event_name,
         Species = species) %>%
  kbl(booktabs = T,
      format.args = list(big.mark = ","),
      caption = "Data summary for single census estimators. M is the number of fish caught in the first sample, marked and returned to the population. n is the number of fish caught in the second sample, and m is the number of marked fish caught in the second sample.") %>%
  kable_styling()
```

```{r abund-data-schn}
N_mods %>%
  select(event_name, species, data) %>%
  distinct() %>%
  unnest(data) %>%
  mutate(across(event_name,
                ~ str_replace(., "_", " "))) %>%
  rename(`Sampling Event` = event_name,
         Species = species,
         Date = date) %>%
  kbl(booktabs = T,
      format.args = list(big.mark = ","),
      caption = "Data summary for multiple census estimators. n is number of fish caught, m is the number of marked fish caught, u is the number of unmarked fish caught, and R is the number of marked fish returned to the population.") %>%
  kable_styling()
```
